\bigskip GRASS GIS Vector State of the Art -- Gearing towards GRASS GIS 7 \bigskip

### 2014-04-21 grassposter/2014_EGU_G7_Landscape/poster.tex
fixed reference
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59868 15284696-431f-4ddb-bdfa-cd5b030d7da7
updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59869 15284696-431f-4ddb-bdfa-cd5b030d7da7

On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology of water availability with lidar-based bathymetric survey and multi-source remote sensing survey [Chemin 2011].\newline
\begin{center}
\includegraphics[width=0.4\textwidth]{images/ofs1}
\hspace{5mm}
\includegraphics[width=0.3\textwidth]{images/ofs2}
\newline
Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [8]
\end{center}
}

\startfourthcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{3D}{
\smallskip
Faces

@@

\begin{center}
\begin{tabular}{cp{1.9\textwidth}}
\begin{minipage}{0.25\textwidth}
\includegraphics[width=2in]{svg_images/OSGeo_project.pdf}
\end{minipage}

>>>>

On-farm water storage study with lidar data in NSW (Australia) developed a full remote sensing monitoring methodology of water availability with lidar-based bathymetric survey and multi-source remote sensing survey [Chemin 2011].\newline
\begin{center}
\includegraphics[width=0.4\textwidth]{images/ofs1}
\hspace{5mm}
\includegraphics[width=0.3\textwidth]{images/ofs2}
\newline
Figure 5: On-Farm-Water-Storage Lidar survey and Depth-Volume-Area surveying [Chemin 2011]
\end{center}
}

\startfourthcolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{3D}{
\smallskip
GRASS 7 has 3D topological capabilities, as described in Figure 5a. An application to buildings is found in Figure 5b.

@@

\begin{center}
\begin{tabular}{cp{1.9\textwidth}}
\begin{minipage}{0.25\textwidth}
\hspace{15mm}
\includegraphics[width=2in]{svg_images/OSGeo_project.pdf}
\end{minipage}
